CommonMind Consortium: DLPFC

### 2020-09-18 combined_analysis/diff.networks.Rmd
Update diff networks

library(WGCNA)
library(variancePartition)
library(decorate)
library(ggrepel)
library(cowplot) 
library(plyr) 
library(qvalue)  
library(BiocParallel)  
}) 
source("../common_functions/common_functions.R")   
# source("common_functions/common_functions.R")

@@

```{r null.results}
p = df_test$P.Value[df_test$Cohort=="MSSM-Penn-Pitt"]
print(1 - qvalue(p)$pi0)
hist(p)

p = df_test$P.Value[df_test$Cohort== "NIMH-HBCC"]
1 - qvalue(p)$pi0
hist(p)
```

>>>>

library(WGCNA)
library(variancePartition)
library(decorate)
library(ggrepel)
library(cowplot) 
library(knitr) 
library(plyr) 
library(qvalue)  
library(BiocParallel)  
}) 
source("../common_functions/common_functions.R")   
# source("common_functions/common_functions.R")

@@

```{r null.results}
p = df_test$P.Value[df_test$Cohort=="MSSM-Penn-Pitt"]
# print(1 - qvalue(p)$pi0)
hist(p)

p = df_test$P.Value[df_test$Cohort== "NIMH-HBCC"]
data.frame(pi1 = 1 - qvalue(p)$pi0, "# DE" = sum(p.adjust(p, 'fdr') < 0.05)) %>% kable
hist(p)
```
